Effect of quality-adjusted production function inputs

### 2015-05-08 Articles/Presentation_ESEE_2015/ESEE_2015.Rnw
Now calculating pre-econometric data.

<<Data, eval=TRUE>>=
dataPT <- filter(IST, Country == "PT")
dataUK <- filter(Leeds, Country == "UK")
historicalData <- plyr::rbind.fill(dataPT, dataUK)
@

<<Time Series Variables>>=
# This block of code sets up the time-series variables 
# to be used for each country.
# Adding this level of abstraction makes it easier 
# for us to change variables later.
# It also makes it easier to see what is going on 
# in each formula throughout the document.
# Use of substitute establishes an R "name"
# that can be a component of a formula.
# Economic output
y_PT <- substitute(iGDP)
y_UK <- substitute(iGDP)
# Portugal undajusted inputs
k_PT_unadj <- substitute(iKstkS.L)
l_PT_unadj <- substitute(iL)
e_PT_unadj <- substitute(iXpMP)
# Portugal quality-adjusted inputs
k_PT_adj <- substitute(iKservS.L)
l_PT_adj <- substitute(ihLest)
e_PT_adj <- substitute(iUMP)
# UK unadjusted inputs
k_UK_unadj <- substitute(iKstkO.WwithRD)
l_UK_unadj <- substitute(iL)
e_UK_unadj <- substitute(iXp)
# UK quality-adjusted inputs
k_UK_adj <- substitute(iKservO.WwithRD)
l_UK_adj <- substitute(ihLest)
e_UK_adj <- substitute(iU)
# Time variables
t_PT <- substitute(iYear)
t_UK <- substitute(iYear)
@

@@

@@

<<Fitted_Data>>=
extract_fitted_comparison <- function(mod, id){
  df <- mod$data[ , c("Year", "iGDP", "Country")]
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadj"){
    df$adjusted <- "Unadjusted"
  } else if (id_list[[2]] == "adj"){
    df$adjusted <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]    
  return(df)
}
fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
fitted_data <- do.call(rbind, fitted_data)
# Melt fitted_data so it can be used for plotting
# Relevel factors before plotting
fitted_data$Country <- relevelFactor(as.factor(fitted_data$Country), c("PT", "UK"))
fitted_data$adjusted <- relevelFactor(as.factor(fitted_data$adjusted), c("Unadjusted", "Quality-adjusted"))
fitted_data$energy <- relevelFactor(as.factor(fitted_data$energy), c("Without energy", "With Energy"))
@

>>>>

<<Data, eval=TRUE>>=
dataPT <- filter(IST, Country == "PT")
dataUK <- filter(Leeds, Country == "UK")
@

<<Time Series Variables>>=
# This block of code sets up the time-series variables 
# to be used for each country.
# Adding this level of abstraction makes it easier 
# for us to change variables later.
# It also makes it easier to see what is going on 
# in each formula throughout the document.
# Use of substitute establishes an R "name"
# that can be a component of a formula.
# Economic output
y_PT <- substitute(iGDP)
y_UK <- substitute(iGDP)
# Portugal undajusted inputs
k_PT_unadj <- substitute(iKstkS.L)
l_PT_unadj <- substitute(iL)
e_PT_unadj <- substitute(iXpMP)
# Portugal quality-adjusted inputs
k_PT_adj <- substitute(iKservS.L)
l_PT_adj <- substitute(ihLest)
e_PT_adj <- substitute(iUMP)
# UK unadjusted inputs
k_UK_unadj <- substitute(iKstkO.WwithRD)
l_UK_unadj <- substitute(iL)
e_UK_unadj <- substitute(iXp)
# UK quality-adjusted inputs
k_UK_adj <- substitute(iKservO.WwithRD)
l_UK_adj <- substitute(ihLest)
e_UK_adj <- substitute(iU)
# Time variables
t_PT <- substitute(iYear)
t_UK <- substitute(iYear)

# Create some pre-econometric ratios
# Unadjusted variables
dataPT <- transform(dataPT, kPerGDP_unadj = eval(k_PT_unadj)/iGDP)
dataPT <- transform(dataPT, lPerGDP_unadj = eval(k_PT_unadj)/iGDP)
dataPT <- transform(dataPT, ePerGDP_unadj = eval(e_PT_unadj)/iGDP)
dataUK <- transform(dataUK, kPerGDP_unadj = eval(k_UK_unadj)/iGDP)
dataUK <- transform(dataUK, lPerGDP_unadj = eval(k_UK_unadj)/iGDP)
dataUK <- transform(dataUK, ePerGDP_unadj = eval(e_UK_unadj)/iGDP)
# Quality-adjusted variables
dataPT <- transform(dataPT, kPerGDP_adj = eval(k_PT_adj)/iGDP)
dataPT <- transform(dataPT, lPerGDP_adj = eval(k_PT_adj)/iGDP)
dataPT <- transform(dataPT, ePerGDP_adj = eval(e_PT_adj)/iGDP)
dataUK <- transform(dataUK, kPerGDP_adj = eval(k_UK_adj)/iGDP)
dataUK <- transform(dataUK, lPerGDP_adj = eval(k_UK_adj)/iGDP)
dataUK <- transform(dataUK, ePerGDP_adj = eval(e_UK_adj)/iGDP)

# Now create the historicalData data frame
historicalData <- plyr::rbind.fill(dataPT, dataUK)
@

@@

<<Pre-econometric graph>>=

@@

<<Fitted_Data>>=
extract_fitted_comparison <- function(mod, id){
  df <- mod$data[ , c("Year", "iGDP", "Country")]
  # Trim fitted to be same length as df to eliminate problems with possible NAs at end of fitted
  df$fitted <- yhat(mod)[c(1:length(df$Year))]
  # Parse the id to find out whether this is quality-adjusted data
  id_list <- strsplit(id, split = "[.]")[[1]]
  if (id_list[[2]] == "unadj"){
    df$adjusted <- "Unadjusted"
  } else if (id_list[[2]] == "adj"){
    df$adjusted <- "Quality-adjusted"
  } else {
    stop("Unknown adjustment.")
  }
  if (id_list[[3]] == "noE"){
    df$energy <- "Without energy"
  } else if (id_list[[3]] == "withE"){
    df$energy <- "With energy"
  } else {
    stop("Unknown energy.")
  }
  df$model <- id_list[[4]]    
  return(df)
}
fitted_data <- leaf_apply(models, extract_fitted_comparison, class=c("CDEmodel", "cesEst", "LINEXmodel"))
# Create a data frame.
fitted_data <- do.call(rbind, fitted_data)
# Melt fitted_data so it can be used for plotting
# Relevel factors before plotting
fitted_data$Country <- relevelFactor(as.factor(fitted_data$Country), c("PT", "UK"))
fitted_data$adjusted <- relevelFactor(as.factor(fitted_data$adjusted), c("Unadjusted", "Quality-adjusted"))
fitted_data$energy <- relevelFactor(as.factor(fitted_data$energy), c("Without energy", "With Energy"))
@
